NeuronUnit: Collaboratively Testing the Validity of Neuroscientific Models

### 2013-11-30 NeurounitFrontiers/Paper.tex

\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
In particular, we will continue to focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}. We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}. \todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Neuroscientists can use these tools to create test suites tailored to specific systems of interest (for example, investigators interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{hippocampus\_tests}, parameterized by relevant data from \textit{NeuroElectro}).

We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop similar repositories that synergistically link \textit{SciUnit} to relevant ongoing standardization efforts and provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain.

\subsection{Models from NeuroML}\label{sec:neuroml_models}
NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
It permits many neurophysiological/neuroanatomical models to be described in a simulator-independent fashion, and executed across many popular simulators due to inter-conversion capabilities of the NeuroML API. 
Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components, exposing potential capabilities. 
It is ideal for model sharing, curation, and for answering both \textit{what} and \textit{how} programatically.

NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
Because NeuroML can describe such a wide range of models, \verbx{NeuroConstructModel} makes few assumptions about them: that each one is \verbx{TimeIntegrable}, and \verbx{HasMembranePotential}.  
It is subclassed to test \textit{specific} NeuroML models (Fig. \ref{fig:ca1_model}).

>>>>

\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}. 
We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}. 
This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}. 
Scientists can use these tools to easily create test suites tailored to specific systems of interest. 
For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus_tests}, parameterized by relevant data from \textit{NeuroElectro}. 
To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository. 
Each community can develop suitable quality standards for merging pull requests. 
Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.
\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}

We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure. Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and curate models in test repositories like \textit{HippocampusTests}. The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that help scientists understand, precisely, the state-of-the-art in their field.

\subsection{Models from NeuroML}\label{sec:neuroml_models}
NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion. 
Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components. We use these facilities to expose capabilities automatically. 
It has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.

NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that have capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}. It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}).
